On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-08 paper/paper.tex
Shrunk figures, but they are appearing out of ordergp
Figures in correct order

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\RequirePackage{amsmath,amssymb}
% \RequirePackage{stmaryrd}
\documentclass[runningheads, a4paper]{llncs}
% \usepackage{biblatex}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
% \usepackage{amsmath}

@@

@@

% \clearpage
\begin{figure*}
  \centering 
  \resizebox{0.8\columnwidth}{10cm}{\includegraphics{Diagrams/Flowchart.pdf}}
  % \includegraphics{Diagrams/Flowchart.pdf}
   \caption{Control Flow of the Core Plugin}
   \label{fig:CorePlugin}
\end{figure*}

@@

\begin{figure*}[hp]

@@

@@

        \ttt{f = $C^{*}\expr{\ttt{externalize ($\lambda \eta \rarr$ runIter ($\lambda \ttt{x} \rarr \ttt{case s of \{ $T'_{\ttt{f}}\exprdots$}$ \}) $\eta$)}}$} & \text{\parbox{5cm}{if \ttt{f} occurs free in \ttt{\{ ... \}}, where $\eta$ is a fresh name}}\\

@@

  &C\expr{\ttt{K x0 ... xN }} \rewrites \ttt{construct (K (unrep $M\expr{\ttt{x0}}$) ... (unrep $M\expr{\ttt{xN}}$))}\;\;\;\;\text{(Where \ttt{K} is a constructor)}\\

@@

% \captionsetup{justification=centering}
\caption{Rewrite rules}
\label{fig:Rewrites}
\end{figure*}

>>>>

%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\RequirePackage{amsmath,amssymb}
% \RequirePackage{stmaryrd}
\documentclass[runningheads, a4paper]{llncs}
% \usepackage{biblatex}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{stmaryrd}
\usepackage{wrapfig}
% \usepackage{amsmath}

@@

\begin{wrapfigure}{R}{0.5\linewidth}
  % \centering
  \resizebox{0.5\columnwidth}{7cm}{\includegraphics{Diagrams/Flowchart.pdf}}
  % \includegraphics{Diagrams/Flowchart.pdf}
   \caption{Control Flow of the Core Plugin}
   \label{fig:CorePlugin}
\end{wrapfigure}%

@@

@@

% \begin{wrapfigure}{r}{0.8\linewidth}
  \begin{wrapfigure}{R}{1.2\linewidth}

@@

\resizebox{1\linewidth}{!}{
  \begin{minipage}{\linewidth}

@@

        \ttt{f = $C^{*}\expr{\ttt{externalize ($\lambda \eta \rarr$ runIter ($\lambda \ttt{x} \rarr \ttt{case s of \{ $T'_{\ttt{f}}\exprdots$}$ \}) $\eta$)}}$} & \text{\parbox{2.4cm}{if \ttt{f} occurs free in \ttt{\{ ... \}}, where $\eta$ is a fresh name}}\\

@@

  &C\expr{\ttt{K x0 ... xN }}\\
    &\quad\rewrites \ttt{construct (K (unrep $M\expr{\ttt{x0}}$) ... (unrep $M\expr{\ttt{xN}}$))}\;\;\;\;\text{(Where \ttt{K} is a constructor)}\\

@@

  \end{minipage}
}%
% }}

% \captionsetup{justification=centering}
\caption{Rewrite rules}
\label{fig:Rewrites}
% \end{wrapfigure}
\end{wrapfigure}
